---
title: "FinalProject"
output: html_document
date: "2023-12-05"
---

```{r}
library(readr)
library(fixest)
library(tidyverse)
library(jtools)
```

```{r}
source("GetData.R")
```

```{r}
MathStats <- data.frame(
  Mean = apply(MathData[, c("age", "studytime", "traveltime", "freetime", "famrel", "goout", "failures", "Medu", "Fedu", "health", "absences", "Dalc", "Walc", "G3")], 2, mean),
  StandardDeviation = apply(MathData[, c("age", "studytime", "traveltime", "freetime", "famrel", "goout", "failures", "Medu", "Fedu", "health", "absences", "Dalc", "Walc", "G3")], 2, sd)
)

print(MathStats)

PortugueseStats <- data.frame(
  Mean = apply(PortugueseData[, c("age", "studytime", "traveltime", "freetime", "famrel", "goout", "failures", "Medu", "Fedu", "health", "absences", "Dalc", "Walc", "G3")], 2, mean),
  StandardDeviation = apply(PortugueseData[, c("age", "studytime", "traveltime", "freetime", "famrel", "goout", "failures", "Medu", "Fedu", "health", "absences", "Dalc", "Walc", "G3")], 2, sd)
)

print(PortugueseStats)
```

```{r}
qplot(x = Medu, y = G3, data = MathData, geom = "jitter") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
qplot(x = Fedu, y = G3, data = MathData, geom = "jitter") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
qplot(x = Medu, y = G3, data = PortugueseData, geom = "jitter") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
qplot(x = Fedu, y = G3, data = PortugueseData, geom = "jitter") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
boxplot(G3 ~ sex, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Sex vs G3", xlab = "Sex", ylab = "G3")
```

```{r}
boxplot(G3 ~ sex, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Sex vs G3", xlab = "Sex", ylab = "G3")
```

```{r}
boxplot(G3 ~ age, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Age vs G3", xlab = "Age", ylab = "G3")
```

```{r}
boxplot(G3 ~ age, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Age vs G3", xlab = "Age", ylab = "G3")
```

```{r}
qplot(x = absences, y = G3, data = MathData, geom = "jitter") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
qplot(x = absences, y = G3, data = PortugueseData, geom = "jitter") +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
boxplot(G3 ~ Walc, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Walc vs G3", xlab = "Walc", ylab = "G3")
```

```{r}
boxplot(G3 ~ Walc, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Walc vs G3", xlab = "Walc", ylab = "G3")
```

```{r}
boxplot(G3 ~ Dalc, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Dalc vs G3", xlab = "Dalc", ylab = "G3")
```

```{r}
boxplot(G3 ~ Dalc, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Dalc vs G3", xlab = "Dalc", ylab = "G3")
```

```{r}
boxplot(G3 ~ goout, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Goout vs G3", xlab = "Goout", ylab = "G3")
```

```{r}
boxplot(G3 ~ goout, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Goout vs G3", xlab = "Goout", ylab = "G3")
```

```{r}
boxplot(G3 ~ reason, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Reason vs G3", xlab = "Reason", ylab = "G3")
```

```{r}
boxplot(G3 ~ reason, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Reason vs G3", xlab = "Reason", ylab = "G3")
```

```{r}
boxplot(G3 ~ romantic, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Romantic vs G3", xlab = "Romantic", ylab = "G3")
```

```{r}
boxplot(G3 ~ romantic, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Romantic vs G3", xlab = "Romantic", ylab = "G3")
```


```{r}
boxplot(G3 ~ famsize, data = MathData, col = "lightblue", border = "black", notch = FALSE, main = "Famsize vs G3", xlab = "Famsize", ylab = "G3")

#Code for bar graphs of sex for each dataset
sex = mathData$sex == "M"
male = 0
female = 0
for(i in 1:length(sex)){
  if (sex[i]){
    male = male + 1
  }
  else{
    female = female + 1
  }
}
barplot(c(male,female), names.arg = c("Male","Female"),ylab = "Frequency",xlab = "Sex", main = "Sex in Math Dataset")
#208 women, 187 men


sex = portData$sex == "M"
male = 0
female = 0
for(i in 1:length(sex)){
  if (sex[i]){
    male = male + 1
  }
  else{
    female = female + 1
  }
}
barplot(c(male,female), names.arg = c("Male","Female"),ylab = "Frequency",xlab = "Sex", main = "Sex in Portuguese Dataset")
#383 women, 266 men

boxplot(G3 ~ famsize, data = PortugueseData, col = "lightblue", border = "black", notch = FALSE, main = "Famsize vs G3", xlab = "Famsize", ylab = "G3")

#Code for histograms of G3
hist(mathData$G3, xlab = "Final Grade", main = "Frequency of Final Grades in Math Dataset")
hist(portData$G3, xlab = "Final Grade", main = "Frequency of Final Grades in Portuguese Dataset")
